Supplement to 'Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-06-29 doc/supplemental.Rmd
added reference to data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

@@

```{r normals}
normals_plot & theme(text = element_text(size = 10))
```

@@

<!-- include contents of `choose_size_var.Rmd` here. -->

<!-- Ask Emilio about citaiton for dataset. -->

@@

Table S2.
Using data from transplant experiments of *Heliconia acuminata* [@brunaExperimentalAssessmentHeliconia2002 <!--# and doi for unpublished data -->] we fit linear regressions with log(leaf area) as the response variable and either log(height), log(shoot number) or log(shoot number x height) as the predictor.
Using the log of size (shoot number $\times$ height) as a predictor gives the lowest AIC, BIC, root mean squared error (RMSE) and highest $R^2$ indicating that it is the best proxy for predicting log(leaf area) as a response.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      dpi = 300)
```

@@

```{r normals, fig.height=4, fig.width=5.5}
normals_plot & theme(text = element_text(size = 10))
```

@@

@@

Table S2.
Using data from transplant experiments of *Heliconia acuminata* [@brunaExperimentalAssessmentHeliconia2002; @brunaLeafNumberLeaf2021] we fit linear regressions with log(leaf area) as the response variable and either log(height), log(shoot number) or log(shoot number x height) as the predictor.
Using the log of size (shoot number $\times$ height) as a predictor gives the lowest AIC, BIC, root mean squared error (RMSE) and highest $R^2$ indicating that it is the best proxy for predicting log(leaf area) as a response.
